### 2021-02-02 priority-cp.tex
Minor layout changes.
started on PCP

We present a correspondence between Priority GV and an updated version of Priority CP~\cite[PCP]{dardhagay18}, which is Wadler's CP~\cite{wadler14} with priorities. The correspondence connects PGV to (a~relaxed variant of) classical linear logic.

\subsection{Revisiting Priority CP}
\begingroup
\usingnamespace{pcp}
Types ($\ty{A}$, $\ty{B}$) in PCP correspond to the connectives of linear logic annotated with priorities $\cs{o}\in\mathbb{N}$. Typing environments, duality, and the priority function $\pr$ are defined as expected (see~\cref{sec:pcp-environments,sec:pcp-duality,sec:pcp-priorities}).
\[
  \begin{array}{lcl}
    \ty{A}, \ty{B}
    & \Coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
Processes ($\tm{P}$, $\tm{Q}$) in PCP are defined by the following grammar.
\[
  \begin{array}[t]{lcl}
    \tm{P}, \tm{Q}
    & \Coloneqq & \tm{\link{x}{y}}
           \sep   \tm{\res{x}{y}{P}}
           \sep   \tm{(\ppar{P}{Q})}
           \sep   \tm{\halt}
    \\   & \sep & \tm{\send{x}{y}{P}}
           \sep   \tm{\close{x}{P}}
           \sep   \tm{\recv{x}{y}{P}}
           \sep   \tm{\wait{x}{P}}
    \\   & \sep & \tm{\inl{x}{P}}
           \sep   \tm{\inr{x}{P}}
           \sep   \tm{\offer{x}{P}{Q}}
           \sep   \tm{\absurd{x}}
  \end{array}
\]
Processes are typed by sequents $\seq{P}{\ty{\Gamma}}$, which correspond to the one-sided sequents classical linear logic. Different from PGV, we do not need to store the greatest priority on the sequent, as, due to the absence of higher-order functions, we cannot compose processes \emph{sequentially}.

PCP decomposes cut into \LabTirName{T-Res} and \LabTirName{T-Par}, and guarantees deadlock freedom using priority constraints, \eg, in \LabTirName{T-Send}. The full typing rules and operational semantics are available in \cref{fig:pcp-operational-semantics-and-typing} and in \cite{dardhagay18}:
\begin{mathpar}
  \inferrule*[lab=T-Res]{
    \seq{P}{\ty{\Gamma},\tmty{x}{A},\tmty{y}{\co{A}}}
  }{\seq{\res{x}{y}{P}}{\ty{\Gamma}}}

  \inferrule*[lab=T-Par]{
    \seq{P}{\ty{\Gamma}}
    \\
    \seq{Q}{\ty{\Delta}}
  }{\seq{\ppar{P}{Q}}{\ty{\Gamma},\ty{\Delta}}}

  \inferrule*[lab=T-Send]{
    \seq{P}{\ty{\Gamma},\tmty{y}{A},\tmty{x}{B}}
    \\
    \cs{o}<\minpr(\ty{\Gamma},\ty{A},\ty{B})
  }{\seq{\send{x}{y}{P}}{\ty{\Gamma},\tmty{x}{\tytens[\cs{o}]{A}{B}}}}
\end{mathpar}

The main change we make to PCP is \emph{removing commuting conversions}. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, using structural congruence.

>>>>

We present a correspondence between Priority GV and an updated version of Priority CP~\cite[PCP]{dardhagay18}, which is Wadler's CP~\cite{wadler14} with priorities. This correspondence connects PGV to (a~relaxed variant of) classical linear logic.

\subsection{Revisiting Priority CP}
\begingroup
\usingnamespace{pcp}
\textbf{Types} ($\ty{A}$, $\ty{B}$) in PCP correspond to linear logic connectives annotated with priorities $\cs{o}\in\mathbb{N}$. Typing environments, duality, and the priority function $\pr(\cdot)$ are defined as expected (see~\cref{sec:pcp-environments,sec:pcp-duality,sec:pcp-priorities}).
\[
  \begin{array}{lcl}
    \ty{A}, \ty{B}
    & \Coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
\textbf{Processes} ($\tm{P}$, $\tm{Q}$) in PCP are defined by the following grammar.
\[
  \begin{array}[t]{lcl}
    \tm{P}, \tm{Q}
    & \Coloneqq & \tm{\link{x}{y}}
           \sep   \tm{\res{x}{y}{P}}
           \sep   \tm{(\ppar{P}{Q})}
           \sep   \tm{\halt}
    \\   & \sep & \tm{\send{x}{y}{P}}
           \sep   \tm{\close{x}{P}}
           \sep   \tm{\recv{x}{y}{P}}
           \sep   \tm{\wait{x}{P}}
    \\   & \sep & \tm{\inl{x}{P}}
           \sep   \tm{\inr{x}{P}}
           \sep   \tm{\offer{x}{P}{Q}}
           \sep   \tm{\absurd{x}}
  \end{array}
\]
Processes are typed by sequents $\seq{P}{\ty{\Gamma}}$, which correspond to the one-sided sequents in classical linear logic. Differently from PGV, in PCP we do not need to store the greatest priority on the sequent, as, due to the absence of higher-order functions, we cannot compose processes \emph{sequentially}.

PCP decomposes cut into \LabTirName{T-Res} and \LabTirName{T-Par} rules---logically corresponding to cycle and mix rules, respectively---and guarantees deadlock freedom by using priority constraints, \eg, as in \LabTirName{T-Send}. The full typing rules and operational semantics are available in \cref{fig:pcp-operational-semantics,fig:pcp-typing} in \cref{app:revisiting-PCP} and in \cite{dardhagay18}:
\begin{mathpar}
  \small
  \inferrule*[lab=T-Res]{
    \seq{P}{\ty{\Gamma},\tmty{x}{A},\tmty{y}{\co{A}}}
  }{\seq{\res{x}{y}{P}}{\ty{\Gamma}}}
  \inferrule*[lab=T-Par]{
    \seq{P}{\ty{\Gamma}}
    \and
    \seq{Q}{\ty{\Delta}}
  }{\seq{\ppar{P}{Q}}{\ty{\Gamma},\ty{\Delta}}}
  \inferrule*[lab=T-Send]{
    \seq{P}{\ty{\Gamma},\tmty{y}{A},\tmty{x}{B}}
    \and
    \cs{o}<\minpr(\ty{\Gamma},\ty{A},\ty{B})
  }{\seq{\send{x}{y}{P}}{\ty{\Gamma},\tmty{x}{\tytens[\cs{o}]{A}{B}}}}
\end{mathpar}

The main change we make to PCP is \emph{removing commuting conversions}. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, but using structural congruence.
